Finite-time Analysis of Frequentist Strategies for Multi-armed Bandits

### 2018-04-18 rebuttal/rebuttal.tex

\documentclass[twoside]{article}
\setlength{\oddsidemargin}{0.25 in}
\setlength{\evensidemargin}{-0.25 in}
\setlength{\topmargin}{-0.6 in}
\setlength{\textwidth}{6.5 in}
\setlength{\textheight}{8.5 in}
\setlength{\headsep}{0.75 in}
\setlength{\parindent}{0 in}
\setlength{\parskip}{0.1 in}

%
% ADD PACKAGES here:
%

\usepackage{amsfonts,graphicx}
%\usepackage{amsmath}
\usepackage{algorithm}
%\usepackage[noend]{algpseudocode}
\usepackage{verbatim}
\usepackage{datetime}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
%\usepackage[margin=1in]{geometry}
\usepackage{natbib}
%\setcitestyle{nocompress}
%\bibpunct{(}{)}{;}{a}{}{,}

% \usepackage[nocompress]{cite}
%\usepackage{graphicx}
%\usepackage[cmex10]{amsmath}
%\usepackage{authblk}
% \usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
\usepackage{macros}
\usepackage{times}

%
% The following commands set up the lecnum (lecture number)
% counter and make various numbering schemes work relative
% to the lecture number.
%
\newcounter{lecnum}
\renewcommand{\thepage}{\arabic{page}}
\renewcommand{\thesection}{\arabic{section}}
\renewcommand{\theequation}{\arabic{equation}}
\renewcommand{\thefigure}{\arabic{figure}}
\renewcommand{\thetable}{\arabic{table}}

%
% The following macro is used to generate the header.
%
\newcommand{\lecture}[4]{
   \pagestyle{myheadings}
   \thispagestyle{plain}
   \newpage
   \setcounter{lecnum}{#1}
   \setcounter{page}{1}
   \noindent
   \begin{center}
   \framebox{
      \vbox{\vspace{2mm}
    %\hbox to 6.28in { {\bf Report on my work with Adobe
		%\hfill Spring 2018} }
       \vspace{4mm}
       \hbox to 6.28in { {\Large \hfill Response to Reviewer Comments on M.S. Thesis \hfill} }
       \vspace{2mm}
       \hbox to 6.28in { \hfill \it{\today} \hfill}
       \vspace{2mm}
       \hbox to 6.28in { \hfill {Name: Subhojyoti Mukherjee} \hfill}
       \vspace{2mm}
       \hbox to 6.28in { \hfill {Roll Number: CS15S300} \hfill}
       \vspace{2mm}
       \hbox to 6.28in { \hfill {Registered for: Master of Science (by Research)} \hfill}
       \vspace{2mm}
       \hbox to 6.28in { \hfill {Guide : Dr. B. Ravindran, Co-Guide : Dr. N. Sudarsanam} \hfill}
       \vspace{2mm}
       }
   }
   \end{center}
   %\markboth{Lecture #1: #2}{Lecture #1: #2}

   \vspace*{4mm}
}

\renewcommand{\cite}[1]{[#1]}
\def\beginrefs{\begin{list}%
        {[\arabic{equation}]}{\usecounter{equation}
         \setlength{\leftmargin}{2.0truecm}\setlength{\labelsep}{0.4truecm}%
         \setlength{\labelwidth}{1.6truecm}}}
\def\endrefs{\end{list}}
\def\bibentry#1{\item[\hbox{[#1]}]}

%Use this command for a figure; it puts a figure in wherever you want it.
%usage: \fig{NUMBER}{SPACE-IN-INCHES}{CAPTION}
\newcommand{\fig}[3]{
			\vspace{#2}
			\begin{center}
			Figure #1:~#3
			\end{center}
	}
% Use these for theorems, lemmas, proofs, etc.
%\newtheorem{theorem}{Theorem}
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{proposition}[theorem]{Proposition}
%\newtheorem{claim}[theorem]{Claim}
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{definition}[theorem]{Definition}
%\newenvironment{proof}{{\bf Proof:}}{\hfill\rule{2mm}{2mm}}

% **** IF YOU WANT TO DEFINE ADDITIONAL MACROS FOR YOURSELF, PUT THEM HERE:

%\newcommand\E{\mathbb{E}}

\begin{document}
\lecture{1}{A - Title}{Lecturer Name}{scribe-name}

\section{Response to Reviewer 1}

We thank the reviewer for his cogent comments and have made a few necessary changes as suggested by the reviewer.

\begin{enumerate}

\item \textbf{Abstract:}

\textit{Correction Suggested:} Start with a transparent sentence.

\textit{Correction Done:} Wrote a more specific sentence outlying the main theme of the thesis.

This thesis studies the following topics in the area of Reinforcement Learning: classic Multi-armed bandits in stationary distribution with the goal of cumulative regret minimization using variance estimates and Thresholding bandits in pure exploration fixed-budget setting with the goal of instantaneous regret minimization also using variance estimates.

\item \textbf{Chapter 1, subsection 1.1 (Introduction to Bandits):}

\textit{Correction Suggested:} "In pursuit of these, the agent can be thought of as making a series of \textit{sequential decisions}" to  "series of tautological decisions".

\textit{Correction Done:} Kept the sentence in original form. It should be a "series of sequential decisions" in the setting considered.

In pursuit of these, the agent can be thought of as making a series of \textit{sequential decisions}...

\item \textbf{Chapter 2, subsection 2.5.2(The Upper Confidence Bound Approach)}

\textit{Correction Suggested:} Break the paragraph, starting from "Empirically...".

\textit{Correction Done:} Wrote it into two paragraphs now.

	UCB-Improved incurs a gap-dependent regret bound of $O\left(\frac{K\log (T\Delta^{2})}{\Delta}\right)$, which is better than that of UCB1. On the other hand, the worst case gap-independent regret bound of UCB-Improved is $O\left(\sqrt{KT\log K}\right)$.

    Empirically, UCB-Improved is out-performed by UCB1 in almost all environments. This stems from the fact that UCB-Improved is pulling all arms equal number of times in each round and hence spends a significant number of pulls in initial exploration as opposed to UCB1 thereby incurring higher regret.

\item \textbf{Chapter 4, subsection 4.1 (Introduction to Thresholding Bandits):}

\textit{Correction Suggested:} Can go to section 1.9.

\textit{Correction Done:} Removed the line that "An interested reader can
read through the previous chapters or can continue from here."

\item \textbf{Chapter 4, subsection 4.2 (Notations and Assumptions):}

\textit{Correction Suggested:} In the sentence "Whenever there is no ambiguity about the underlaying...." correct "underlaying"

\textit{Correction Done:} Corrected the spelling to, "Whenever there is no ambiguity about the underlying...."

\item \textbf{Chapter 4, subsection 4.6 (Challenges in the TBP seeting):}

\textit{Correction Suggested:} Write more succinctly.

\textit{Correction Done:} Rewrote the paragraph.

Further, if we look closely into the TBP setting we will see that there are several similarities between the challenges in SMAB setting and the TBP setting. These challenges are as follows:-

\begin{enumerate}
\item The more closer an arm’s expected reward mean ($r_i$) is  to $\tau$, the more harder is the problem. This stems from the fact that it becomes increasingly difficult to discriminate between the arms lying above and below $\tau$.
\item Lesser the budget $T$, the more harder is the problem. This is because there are lesser number of pulls available and so the number of samples collected tends to be low.
\item The higher the variance of an arm’s reward distribution $D_i$, the more harder is the problem. This is similar to the first case as it becomes harder to discriminate between the arms lying close to the threshold.
\end{enumerate}

\item  \textbf{Chapter 5, subsection 5.1 (Introduction):}

\textit{Correction Suggested:} Capitalize proper nouns such as "section 1"  to "Section 1", "chapter 1" to "Chapter 1", "table 1" to "Table 1" and "figure 1" to "Figure 1".

\textit{Correction Done:} Rewrote all such usages in the thesis.

The rest of the chapter is organized as follows. We elaborate our contributions in Section~5.2 and  we present the AugUCB algorithm in Section~5.3. Our main theoretical result on expected loss is stated in Section~5.4. Section~5.5 contains numerical simulations on various testbeds to show the performance of AugUCB against state-of-the-art algorithms and finally, we summarize in Section~5.6.

\item \textbf{Chapter 5, subsection 5.4 (Proofs):}

\textit{Correction Suggested:} Proofs can be non-italics format style.

\textit{Correction Done:} I did not tamper with the format specified for MS Thesis, so kept the proof format style unchanged.

\item \textbf{Chapter 6, subsection 6.1 (Conclusions):}

\textit{Correction Suggested:} Some word changes.

\textit{Correction Done:} Rewrote the paragraph with the changes..

In this thesis, we studied two different bandit problems, the stochastic multi-armed bandit (SMAB) with the goal of cumulative regret minimization and pure exploration stochastic thresholding bandit problem (TBP) with the goal of expected loss minimization. For the first problem, we devised a novel algorithm called Efficient UCB Variance (EUCBV) which enjoys an order optimal regret bound and performs very well in diverse stochastic environments. In the second part, the thresholding bandit problem, we came up with the novel algorithm called Augmented UCB (AugUCB) which is the first algorithm to use variance estimation for the considered TBP setting and also empirically outperforms most of the other algorithms.

\end{enumerate}

\end{document}

### 2018-04-18 Chapter1/outline.tex
Latest on 8/1/2017
Latest on 18/4/2018

In this chapter, we gave an overview of the various types of bandits available in the literature and also discussed about the main objectives of the thesis and our contributions. In this section, we give a general outline of the thesis that is to follow. In chapter \ref{chap:SMAB} we give a detailed overview of the stochastic multi-armed bandit model and the latest available algorithms in this setting. In the next chapter \ref{chap:EUCBV} we introduce our algorithm Efficient UCB Variance (EUCBV) for the stochastic multi-armed bandit model. We give theoretical guarantees on the performance of EUCBV and also show in numerical simulations that it indeed performs very well as compared to the state-of-the-art algorithms. In the subsequent chapter \ref{chap:tbandit1} we introduce a new variant of pure exploration multi-armed stochastic bandit called the thresholding bandit problem. We analyze the connections between thresholding bandit problem and pure exploration problem and also discuss several existing algorithms in both the settings that are relevant to carefully analyze the thresholding bandit problem. Then in chapter \ref{chap:tbandit2} we introduce our solution for the thresholding bandit problem, called the Augemented UCB (AugUCB) algorithm. We analyze our algorithm AugUCB and derive theoretical guarantees for it as well as show in numerical experiments that it indeed outperforms several state-of-the-art algorithms in the thresholding bandit setting. Finally, in chapter \ref{ThesisConc} we conclude by briefly summarizing all the problems covered in the thesis and discussing some future directions in which the stated problems can be further extended.

>>>>

In this chapter, we gave an overview of the various types of bandits available in the literature and also discussed about the main objectives of the thesis and our contributions. In this section, we give a general outline of the thesis that is to follow. In Chapter \ref{chap:SMAB} we give a detailed overview of the stochastic multi-armed bandit model and the latest available algorithms in this setting. In the next Chapter \ref{chap:EUCBV} we introduce our algorithm Efficient UCB Variance (EUCBV) for the stochastic multi-armed bandit model. We give theoretical guarantees on the performance of EUCBV and also show in numerical simulations that it indeed performs very well as compared to the state-of-the-art algorithms. In the subsequent Chapter \ref{chap:tbandit1} we introduce a new variant of pure exploration multi-armed stochastic bandit called the thresholding bandit problem. We analyze the connections between thresholding bandit problem and pure exploration problem and also discuss several existing algorithms in both the settings that are relevant to carefully analyze the thresholding bandit problem. Then in Chapter \ref{chap:tbandit2} we introduce our solution for the thresholding bandit problem, called the Augmented UCB (AugUCB) algorithm. We analyze our algorithm AugUCB and derive theoretical guarantees for it as well as show in numerical experiments that it indeed outperforms several state-of-the-art algorithms in the thresholding bandit setting. Finally, in Chapter \ref{ThesisConc} we conclude by briefly summarizing all the problems covered in the thesis and discussing some future directions in which the stated problems can be further extended.

### 2018-04-18 Chapter2/intro.tex
Latest on 26/11/2017
Latest on 27/11/2017
Latest on 18/4/2018

In this chapter, we deal with the stochastic multi-armed bandit (SMAB) setting. In its classical form, stochastic MABs represent a sequential learning problem where a learner is exposed to a finite set of actions (or arms) and needs to choose one of the actions at each timestep. After choosing (or pulling) an arm the learner receives a reward, which is conceptualized as an independent random draw from stationary distribution associated with the selected arm. Also, note that in SMAB, the distribution associated with each arm is fixed throughout the entire duration of the horizon denoted by $T$.

@@

The rest of the chapter is organized as follows. We specify all the notations and assumptions in section~\ref{sec:notations}. Then we define the problem statement for the SMAB setting in section~\ref{sec:probDef}. In the next section~\ref{sec:motivation} we discuss the motivations behind the SMAB setting. In section~\ref{sec:related} we discuss extensively on the various state-of-the-art algorithms available for the SMAB setting. Finally, we draw our conclusions in section \ref{chap2:conc}.

>>>>

In this chapter, we deal with the stochastic multi-armed bandit (SMAB) setting. In its classical form, stochastic MABs represent a sequential learning problem where a learner is exposed to a finite set of actions (or arms) and needs to choose one of the actions at each timestep. After choosing (or pulling) an arm the learner receives a reward, which is conceptualized as an independent random draw from stationary distribution associated with the selected arm. Also, note that in SMAB, the distribution associated with each arm is fixed throughout the entire duration of the horizon denoted by $T$. This SMAB formulation is shown in algorithm \ref{alg:SMAB}.

@@

The rest of the chapter is organized as follows. We specify all the notations and assumptions in Section~\ref{sec:notations}. Then we define the problem statement for the SMAB setting in Section~\ref{sec:probDef}. In the next Section~\ref{sec:motivation} we discuss the motivations behind the SMAB setting. In Section~\ref{sec:related} we discuss extensively on the various state-of-the-art algorithms available for the SMAB setting. Finally, we summarize in Section \ref{chap2:conc}.

### 2018-04-18 Chapter2/probDef.tex
Latest on 26/11/2017
Latest on 13/1/2017
Latest on 18/4/2018

With the formulation of SMAB stated in algorithm \ref{alg:SMAB}, the learner seeks to identify the optimal arm as quickly as possible to maximize its rewards. In the pursuit of this, the learner faces the task of balancing exploitation and exploration. In other words, should the learner pull the arm which currently has the best-known estimates (exploit) or explores arms more thoroughly to ensure that a correct decision is being made. This is termed as the \textit{exploration-exploitation dilemma}, one of the fundamental challenges of reinforcement learning as discussed in chapter \ref{chap:intro}.

    The objective of the learner in the SMAB setting is to maximize his rewards or in other words, to minimize the cumulative regret, which is defined as follows:
\begin{align*}
R_{T}=r^{*}T - \sum_{i\in \A} r_{i}z_{i}(T),
\end{align*}
where $T$ is the number of timesteps, and  $z_{i}(T)$ is the number of times the algorithm has chosen arm $i$ up to timestep $T$.
The expected regret of an algorithm after $T$ timesteps can be written as,
\begin{align*}
\E[R_{T}]= \sum_{i=1}^{K} \E[z_i (T)] \Delta_i,
\end{align*}
where $\Delta_{i}=r^{*}-r_{i}$ is the gap between the means of the optimal arm and the $i$-th arm. In the theoretical analysis of each algorithm, we try to obtain bounds on this cumulative regret. These bounds can be both asymptotic or for a finite horizon. Again, these regret bounds can be either gap-dependent or gap-independent bounds.

>>>>

With the formulation of SMAB stated in Algorithm \ref{alg:SMAB}, the learner seeks to identify the optimal arm as quickly as possible to maximize its rewards. In the pursuit of this, the learner faces the task of balancing exploitation and exploration. In other words, should the learner pull the arm which currently has the best-known estimates (exploit) or explores arms more thoroughly to ensure that a correct decision is being made. This is termed as the \textit{exploration-exploitation dilemma}, one of the fundamental challenges of reinforcement learning as discussed in chapter \ref{chap:intro}.

    The objective of the learner in the SMAB setting is to maximize his rewards or in other words, to minimize the cumulative regret, which is defined as follows:
\begin{align*}
R_{T}=r^{*}T - \sum_{i=1}^{K} r_{i}z_{i}(T),
\end{align*}
where $T$ is the number of timesteps, and  $z_{i}(T)$ is the number of times the algorithm has chosen arm $i$ up to timestep $T$.
The expected regret of an algorithm after $T$ timesteps can be written as,
\begin{align*}
\E[R_{T}]= \sum_{i=1}^{K} \E[z_i (T)] \Delta_i,
\end{align*}
where $\Delta_{i}=r^{*}-r_{i}$ is the gap between the means of the optimal arm and the $i$-th arm. In the theoretical analysis of each algorithm, we try to obtain bounds on this cumulative regret. These bounds can be both asymptotic or for a finite horizon. Again, these regret bounds can be either gap-dependent or gap-independent bounds.

### 2018-04-18 Chapter2/related.tex
Latest on 18/4/2018

    One of the earliest among these algorithms is UCB1 algorithm proposed first in \citet{agrawal1995sample} and subsequently analyzed in \citet{auer2002finite}. The UCB1 algorithm (as stated in \citet{auer2002finite}) is mentioned in algorithm \ref{alg:ucb1}.

@@

    The UCB-Improved  stated in algorithm \ref{alg:ucbi}, proposed in \citet{auer2010ucb}, is a round-based variant of UCB1. An algorithm is \textit{round-based} if it pulls all the arms equal number of times in each round and then eliminates one or more arms that it deems to be sub-optimal. Note, that in this algorithm the confidence interval term is $\sqrt{\dfrac{\log{( T\epsilon_{m}^{2})}}{2 n_{m}}}$ which is constant in the $m$-th round as $n_m$ is fixed for that round and all arms are being pulled an equal number of times in each round. This is unlike UCB1 algorithm where the confidence interval term depends on $z_i$ which is a random variable. Also, note that in UCB-Improved the knowledge of horizon is required before-hand to calculate the confidence intervals whereas no such input is required for UCB1. An illustrative flowchart depicting the main steps is given in Figure \ref{fig:ucbimp}.

@@

    UCB-Improved incurs a gap-dependent regret bound of $O\left(\frac{K\log (T\Delta^{2})}{\Delta}\right)$, which is better than that of UCB1. On the other hand, the worst case gap-independent regret bound of UCB-Improved is $O\left(\sqrt{KT\log K}\right)$.Empirically, UCB-Improved is out-performed by UCB1 in almost all environments. This stems from the fact that UCB-Improved is pulling all arms equal number of times in each round and hence spends a significant number of pulls in initial exploration as opposed to UCB1 thereby incurring higher regret.

@@

    In the later work of \citet{audibert2009minimax}, the authors propose the MOSS algorithm which stands for Minimax Optimal Strategy in the Stochastic case (see algorithm \ref{alg:moss}). The confidence interval of MOSS is designed in such a way so as to divide the horizon $T$ proportionally between the number of arms $K$ and the number of pulls $z_i$ that each arm is pulled. As the sub-optimal arms are pulled more number of times their confidence interval decreases, indicating that they have been explored sufficiently, forcing MOSS to explore other arms and quickly converging on the optimal arm. Theoretically, \citet{audibert2009minimax}  showed that the worst case gap-independent regret bound of MOSS is $O\left( \sqrt{KT} \right)$ which improves upon UCB1 by a factor of order $\sqrt{\log T}$. However, the gap-dependent regret of MOSS is $O\left( \frac{K^{2}\log\left(T\Delta^{2}/K\right)}{\Delta}\right)$ and in certain regimes, this can be worse than even UCB1 (see \citet{audibert2009minimax,lattimore2015optimally}).

@@

Recently in \citet{lattimore2015optimally}, the authors proposed the Optimally Confident UCB (OCUCB) (see algorithm \ref{alg:ocucb}) which incorporates the increasing timestep $t$ in the confidence interval along with the fixed horizon $T$ and exploration parameters $\psi$ and $\alpha$. The authors showed that the algorithm OCUCB achieves order-optimal gap-dependent regret bound of $O\left(\sum_{i=2}^{K}\frac{\log\left(T/H_i\right)}{\Delta_i}\right)$ where $H_i=\sum_{j=1}^{K}\min\left\lbrace \frac{1}{\Delta_i^2},\frac{1}{\Delta_j^2}\right\rbrace$, and a gap-independent regret bound of $O\left( \sqrt{KT}\right)$. This is the best known gap-dependent and gap-independent regret bounds in the stochastic MAB framework. However, unlike our proposed EUCBV algorithm (in chapter \ref{chap:EUCBV}), OCUCB does not take into account the variance of the arms; as a result, empirically  we find  that our algorithm outperforms OCUCB in all the environments considered.

@@

    In contrast to the above work, the UCB-Variance (UCBV) algorithm in \citet{audibert2009exploration} utilizes variance estimates to compute the confidence intervals for each arm. In UCBV (see algorithm \ref{alg:ucbv}) the confidence interval term is given by $\sqrt{\dfrac{2\hat{v}_i\log (t)}{s_i}} + \dfrac{3\log (t)}{3}$ where $\hat{v}_i$ denotes the empirical variance of the arm $i$. Hence, the confidence interval makes sure that the arms whose variances are high are pulled more often to get a better estimates of their $\hat{r}_i$.

@@

    Another notable design principle which has recently gained a lot of popularity is the Thompson Sampling (TS) algorithm (\citep{thompson1933likelihood}, \citep{agrawal2011analysis})  and  Bayes-UCB (BU) algorithm \citep{kaufmann2012bayesian}. This TS is stated in algorithm \ref{alg:ts}. The TS algorithm is initialized with a uniform prior and it maintains a posterior reward distribution for each arm; at each round, the algorithm samples values from these distributions and the arm corresponding to the highest sample value is chosen. Although TS is found to perform extremely well when the reward distributions are Bernoulli, it is established that with Gaussian priors the worst-case regret can be as bad as $\Omega \left( \sqrt{KT\log T}\right)$ \citep{lattimore2015optimally}. The BU algorithm is an extension of the TS algorithm that takes quartile deviations into consideration while choosing arms.

>>>>

    One of the earliest among these algorithms is UCB1 algorithm proposed first in \citet{agrawal1995sample} and subsequently analyzed in \citet{auer2002finite}. The UCB1 algorithm (as stated in \citet{auer2002finite}) is mentioned in Algorithm \ref{alg:ucb1}.

@@

    The UCB-Improved  stated in Algorithm \ref{alg:ucbi}, proposed in \citet{auer2010ucb}, is a round-based variant of UCB1. An algorithm is \textit{round-based} if it pulls all the arms equal number of times in each round and then eliminates one or more arms that it deems to be sub-optimal. Note, that in this algorithm the confidence interval term is $\sqrt{\dfrac{\log{( T\epsilon_{m}^{2})}}{2 n_{m}}}$ which is constant in the $m$-th round as $n_m$ is fixed for that round and all arms are being pulled an equal number of times in each round. This is unlike UCB1 algorithm where the confidence interval term depends on $z_i$ which is a random variable. Also, note that in UCB-Improved the knowledge of horizon is required before-hand to calculate the confidence intervals whereas no such input is required for UCB1. An illustrative flowchart depicting the main steps is given in Figure \ref{fig:ucbimp}.

@@

    UCB-Improved incurs a gap-dependent regret bound of $O\left(\frac{K\log (T\Delta^{2})}{\Delta}\right)$, which is better than that of UCB1. On the other hand, the worst case gap-independent regret bound of UCB-Improved is $O\left(\sqrt{KT\log K}\right)$.

    Empirically, UCB-Improved is out-performed by UCB1 in almost all environments. This stems from the fact that UCB-Improved is pulling all arms equal number of times in each round and hence spends a significant number of pulls in initial exploration as opposed to UCB1 thereby incurring higher regret.

@@

    In the later work of \citet{audibert2009minimax}, the authors propose the MOSS algorithm which stands for Minimax Optimal Strategy in the Stochastic case (see Algorithm \ref{alg:moss}). The confidence interval of MOSS is designed in such a way so as to divide the horizon $T$ proportionally between the number of arms $K$ and the number of pulls $z_i$ that each arm is pulled. As the sub-optimal arms are pulled more number of times their confidence interval decreases, indicating that they have been explored sufficiently, forcing MOSS to explore other arms and quickly converging on the optimal arm. Theoretically, \citet{audibert2009minimax}  showed that the worst case gap-independent regret bound of MOSS is $O\left( \sqrt{KT} \right)$ which improves upon UCB1 by a factor of order $\sqrt{\log T}$. However, the gap-dependent regret of MOSS is $O\left( \frac{K^{2}\log\left(T\Delta^{2}/K\right)}{\Delta}\right)$ and in certain regimes, this can be worse than even UCB1 (see \citet{audibert2009minimax,lattimore2015optimally}).

@@

Recently in \citet{lattimore2015optimally}, the authors proposed the Optimally Confident UCB (OCUCB) (see Algorithm \ref{alg:ocucb}) which incorporates the increasing timestep $t$ in the confidence interval along with the fixed horizon $T$ and exploration parameters $\psi$ and $\alpha$. The authors showed that the algorithm OCUCB achieves order-optimal gap-dependent regret bound of $O\left(\sum_{i=2}^{K}\frac{\log\left(T/H_i\right)}{\Delta_i}\right)$ where $H_i=\sum_{j=1}^{K}\min\left\lbrace \frac{1}{\Delta_i^2},\frac{1}{\Delta_j^2}\right\rbrace$, and a gap-independent regret bound of $O\left( \sqrt{KT}\right)$. This is the best known gap-dependent and gap-independent regret bounds in the stochastic MAB framework. However, unlike our proposed EUCBV algorithm (in Chapter \ref{chap:EUCBV}), OCUCB does not take into account the variance of the arms; as a result, empirically  we find  that our algorithm outperforms OCUCB in all the environments considered.

@@

    In contrast to the above work, the UCB-Variance (UCBV) algorithm in \citet{audibert2009exploration} utilizes variance estimates to compute the confidence intervals for each arm. In UCBV (see Algorithm \ref{alg:ucbv}) the confidence interval term is given by $\sqrt{\dfrac{2\hat{v}_i\log (t)}{s_i}} + \dfrac{3\log (t)}{3}$ where $\hat{v}_i$ denotes the empirical variance of the arm $i$. Hence, the confidence interval makes sure that the arms whose variances are high are pulled more often to get a better estimates of their $\hat{r}_i$.

@@

    Another notable design principle which has recently gained a lot of popularity is the Thompson Sampling (TS) algorithm (\citep{thompson1933likelihood}, \citep{agrawal2011analysis})  and  Bayes-UCB (BU) algorithm \citep{kaufmann2012bayesian}. This TS is stated in Algorithm \ref{alg:ts}. The TS algorithm is initialized with a uniform prior and it maintains a posterior reward distribution for each arm; at each round, the algorithm samples values from these distributions and the arm corresponding to the highest sample value is chosen. Although TS is found to perform extremely well when the reward distributions are Bernoulli, it is established that with Gaussian priors the worst-case regret can be as bad as $\Omega \left( \sqrt{KT\log T}\right)$ \citep{lattimore2015optimally}. The BU algorithm is an extension of the TS algorithm that takes quartile deviations into consideration while choosing arms.

### 2018-04-18 Chapter3/introduction.tex
Latest on 18/4/2018

    The rest of the chapter is organized as follows. We elaborate our contributions in section~\ref{sec:contri} and in section~\ref{sec:eucbv} we present the  EUCBV algorithm. Our main theoretical results are stated in section~\ref{sec:results}, while the proofs are established in section \ref{sec:proofTheorem}. Section~\ref{sec:expt} contains results and discussions from our numerical experiments and finally we summarize in section \ref{sec:conc}.
    %and Appendix \ref{sec:app:EUCBV} contains the proofs of the lemmas that have been used for proving the main result.

>>>>

    The rest of the chapter is organized as follows. We elaborate our contributions in Section~\ref{sec:contri} and in Section~\ref{sec:eucbv} we present the  EUCBV algorithm. Our main theoretical results are stated in Section~\ref{sec:results}, while the proofs are established in Section~\ref{sec:proofTheorem}. Section~\ref{sec:expt} contains results and discussions from our numerical experiments and finally we summarize in Section \ref{sec:conc}.
    %and Appendix \ref{sec:app:EUCBV} contains the proofs of the lemmas that have been used for proving the main result.

### 2018-04-18 Chapter4/connection.tex
Latest on 27/11/2017
Latest on 18/4/2018

The thresholding bandit problem is a specific instance of the pure-exploration setup of \citet{chen2014combinatorial}. To put it in perspective, the considered TBP setup lies at the intersection of the larger pure exploration setting and the stochastic multi-armed bandit (SMAB) setting discussed in chapter \ref{chap:SMAB} and chapter \ref{chap:EUCBV}. This is shown in Figure \ref{fig:con}.

@@

Further, if we look closely into the TBP setting we will see that there are several similarities between the challenges in SMAB setting and the TBP setting.

\begin{enumerate}
\item Closer an arm’s expected reward mean ($r_i$) to $\tau$ $\Rightarrow$ Harder is the problem. This stems from the fact that it becomes increasingly difficult to discriminate between the arms lying above and below $\tau$.
\item Lesser the budget $T$ $\Rightarrow$ Harder is the problem. This is because there are lesser number of pulls available and so the number of samples collected tends to be low.
\item Higher the variance of an arm’s reward distribution $D_i$ $\Rightarrow$ Harder is the problem. This is similar to the first case as it becomes harder to discriminate between the arms lying close to the threshold.
\end{enumerate}

In the theoretical section in chapter \ref{chap:tbandit2} we will try to characterize this hardness and give guarantees that are almost optimal.

>>>>

The thresholding bandit problem is a specific instance of the pure-exploration setup of \citet{chen2014combinatorial}. To put it in perspective, the considered TBP setup lies at the intersection of the larger pure exploration setting and the stochastic multi-armed bandit (SMAB) setting discussed in Chapter \ref{chap:SMAB} and Chapter \ref{chap:EUCBV}. This is shown in Figure \ref{fig:con}.

@@

Further, if we look closely into the TBP setting we will see that there are several similarities between the challenges in SMAB setting and the TBP setting. These challenges are as follows:-

\begin{enumerate}
\item The more closer an arm’s expected reward mean ($r_i$) is  to $\tau$, the more harder is the problem. This stems from the fact that it becomes increasingly difficult to discriminate between the arms lying above and below $\tau$.
\item Lesser the budget $T$, the more harder is the problem. This is because there are lesser number of pulls available and so the number of samples collected tends to be low.
\item The higher the variance of an arm’s reward distribution $D_i$, the more harder is the problem. This is similar to the first case as it becomes harder to discriminate between the arms lying close to the threshold.
\end{enumerate}

In the theoretical section in Chapter \ref{chap:tbandit2} we will try to characterize this hardness and give guarantees that are almost optimal.

### 2018-04-18 Chapter4/intro.tex
Latest on 18/4/2018

In the previous chapters \ref{chap:SMAB} and \ref{chap:EUCBV} we studied the stochastic multi-armed bandit (SMAB) setting with the goal of minimizing cumulative regret. In this chapter, we will study another setting called Pure-exploration multi-armed bandits. An interested reader can read through the previous chapters or can continue from here. Though we re-use the ideas from SMABs, the goal of pure exploration setup is distinctly different from that of cumulative regret minimization of SMABs and the required algorithms to understand this setup are mentioned in this chapter itself. Pure-exploration MAB problems are unlike their traditional (exploration vs.\ exploitation)  counterparts, the SMABs, where the objective is to minimize the cumulative regret. The cumulative regret is the total loss incurred by the learner for not playing the optimal arm throughout the time horizon $T$. 
    In pure-exploration problems a learning algorithm, until time $T$, can invest entirely on exploring the arms without being concerned about the loss incurred while exploring; the objective is to minimize the probability that the arm recommended at time $T$ is not the best arm.  In this chapter, we further consider a combinatorial version of the pure-exploration MAB, called the thresholding bandit problem (TBP).  Here, the learning algorithm is provided with a threshold $\tau$, and the objective, after exploring for $T$ rounds, is to output all arms $i$ whose $r_{i}$ is above $\tau$. 
It is important to emphasize that the \emph{thresholding} bandit problem is different from the \emph{threshold} bandit setup studied in \cite{abernethy2016threshold}, where the learner receives a unit reward whenever the value of an observation is above a threshold.

    The rest of the chapter is organized as follows. We specify all the notations and assumptions in section~\ref{tbandit:notations}. Then we define the problem statement for the TBP setting in section~\ref{tbandit:probDef}. In the next section~\ref{tbandit:motivation} we discuss the motivations behind the TBP setting. In section~\ref{tbandit:prevRes} we discuss extensively on the various state-of-the-art algorithms available for the pure exploration setting, in section~\ref{tbandit:connection} we draw the connection between pure exploration and thresholding bandit setting and then in section~\ref{tbandit:prevResAPT} we discuss the latest works done in the TBP setting. Finally, we summarize in section \ref{tbandit:conc}.

>>>>

In the previous Chapter \ref{chap:SMAB} and Chapter \ref{chap:EUCBV} we studied the stochastic multi-armed bandit (SMAB) setting with the goal of minimizing cumulative regret. In this chapter, we will study another setting called Pure-exploration multi-armed bandits. Though we re-use the ideas from SMABs, the goal of pure exploration setup is distinctly different from that of cumulative regret minimization of SMABs and the required algorithms to understand this setup are mentioned in this chapter itself. Pure-exploration MAB problems are unlike their traditional (exploration vs.\ exploitation)  counterparts, the SMABs, where the objective is to minimize the cumulative regret. The cumulative regret is the total loss incurred by the learner for not playing the optimal arm throughout the time horizon $T$. 
    In pure-exploration problems a learning algorithm, until time $T$, can invest entirely on exploring the arms without being concerned about the loss incurred while exploring; the objective is to minimize the probability that the arm recommended at time $T$ is not the best arm.  In this chapter, we further consider a combinatorial version of the pure-exploration MAB, called the thresholding bandit problem (TBP).  Here, the learning algorithm is provided with a threshold $\tau$, and the objective, after exploring for $T$ rounds, is to output all arms $i$ whose $r_{i}$ is above $\tau$. 
It is important to emphasize that the \emph{thresholding} bandit problem is different from the \emph{threshold} bandit setup studied in \cite{abernethy2016threshold}, where the learner receives a unit reward whenever the value of an observation is above a threshold.

%An interested reader can read through the previous chapters or can continue from here.

    The rest of the chapter is organized as follows. We specify all the notations and assumptions in Section~\ref{tbandit:notations}. Then we define the problem statement for the TBP setting in Section~\ref{tbandit:probDef}. In the next Section~\ref{tbandit:motivation} we discuss the motivations behind the TBP setting. In Section~\ref{tbandit:prevRes} we discuss extensively on the various state-of-the-art algorithms available for the pure exploration setting, in Section~\ref{tbandit:connection} we draw the connection between pure exploration and thresholding bandit setting and then in Section~\ref{tbandit:prevResAPT} we discuss the latest works done in the TBP setting. Finally, we summarize in Section~\ref{tbandit:conc}.
